ROS controller for IRIS+
========================

A small guide to setting up and running this project.

\#\# Install ROS

Follow the [official instructions](http://wiki.ros.org/indigo/Installation/Ubuntu) for ROS Indigo.
After configuring the Ubuntu repositories and keys, this includes installing the full desktop install via
~~~~
sudo apt-get install ros-indigo-desktop-full
~~~~
(This might download more than 1GB of packages)

Then initialize  rosdep 
~~~~
sudo rosdep init
rosdep update
~~~~

Make sure the ROS environment variables are set when bash-terminals are launched.
To do this, add  source /opt/ros/indigo/setup.bash .
You can do this, by executing
~~~~
echo "source /opt/ros/indigo/setup.bash" >> ~/.bashrc
source ~/.bashrc
~~~~
in a terminal window.

The installation of rosinstall (package  python-rosinstall ) is not required.

\#\# Setup Workspace

(for more detailed instructions see the [official ROS tutorial](http://wiki.ros.org/ROS/Tutorials/InstallingandConfiguringROSEnvironment)).
Create a workspace folder and make sure it contains a folder named  src .
In this  src  folder run  catkin\_init\_workspace  and make sure this directory is in the  ROS\_PACKAGE\_PATH  variable.
You can check this with  echo \$ROS\_PACKAGE\_PATH .
If the directory is missing (which is likely), add the line
~~~~
export ROS\_PACKAGE\_PATH=~/[your ros workspace]/src:\${ROS\_PACKAGE\_PATH}
~~~~
to the file  ~/.bashrc .

Copy the relevant folders (currently  guad\_control ,  mavros  and  gui ) into the  src  folder.
To make sure that you mavros can access your USB port, you might need to add your user to the group  dialout  by executing  sudo usermod -a -G dialout \$USER .

Install the ROS control toolbox
 sudo apt-get install ros-indigo-control-toolbox 


Do NOT do this:
Make sure mavros is installed ( sudo apt-get install ros-indigo-mavros ) and run

\#\# Build Project

~~~~
catkin\_make
~~~~

\#\# Run Project

\#\#\# Without Mavros

In two terminal windows (both in the workspace root), run
~~~~
source ./devel/setup.bash
roslaunch quad\_control iris1.launch
~~~~
and
~~~~
source ./devel/setup.bash
rqt --standalone  tabbedGUI --args Iris1/
~~~~

\#\#\# With Mavros

If you want to connect to an actual quadcopter, run the following three blocks, each in his own terminal window in the workspace root:
~~~~
source ./devel/setup.bash
roslaunch quad\_control iris1\_mavros.launch
~~~~
,
~~~~
source ./devel/setup.bash
roslaunch mavros apm2.launch
~~~~
and 
~~~~
source ./devel/setup.bash
rqt --standalone  tabbedGUI --args Iris1/
~~~~

\#\# Uninstall ROS

Only if needed:

To uninstall ROS and remove all configuration files, execute the following commands
~~~~
sudo apt-get purge ros-indigo*
sudo apt-get purge python-rosdep python-rospkg python-rosinstall
sudo apt-get autoremove
~~~~
and remove all lines in  ~/.bashrc  concerning ROS.
